Even-point Multi-loop Unitarity and its Applications: Exponentiation, Anomalies and Evanescence

### 2023-07-07 eventPointTwoLoop.tex
some typos

@@

\begin{equation}\label{eq:NLSMDunce}
\begin{aligned}
\text{Cut}\left(\! \scaleIntBscalarsmall{1}{2}{3}{4} \! \right)&=\sum_{\text{states}}\mathcal{A}^{\text{NLSM}}_{(2|q_4\bar{q}_3|\bar{q}_1)}\mathcal{A}^{\text{NLSM}}_{(1|\bar{q}_4q_3|\bar{q}_2)}\mathcal{A}^{\text{NLSM}}_{(q_2|34|q_1)}
\\
&=C^{\text{Xbox}}_{([12]|34)}\left[\tau^{(3)}_1 \tau^{(2)}_3\tau^{(1)}_4+\tau^{(3)}_1 \tau^{(2)}_4\tau^{(1)}_3+\tau^{(3)}_2 \tau^{(2)}_3\tau^{(1)}_4+\tau^{(3)}_2 \tau^{(2)}_4\tau^{(1)}_3\right]
\\
&-\left(C^{\text{2box}}_{(12|34)}\tau^{(3)}_1+C^{\text{2box}}_{(12|43)}\tau^{(3)}_2\right) \left[ \tau^{(2)}_3\tau^{(1)}_3+ \tau^{(2)}_4\tau^{(1)}_4\right] \,.
\end{aligned}
\end{equation}
The kinematic variables $\tau^{(i)}_j $ and $\tau_{ij}$ are the same, except we have made the replacement $p_i \rightarrow q_i$. The full two-loop NLSM amplitude can thus be computed by summing over the distinct labels of the resulting integrals, each weighted by suitable internal symmetry factors:
\begin{equation}
\label{eq:NLSM2loop}
\mathcal{A}^{\text{NLSM}}_{\text{2-loop}}=\frac{1}{4}\left[ \scaleIntCsmall \right]+ \frac{1}{2}\left[\scaleIntBscalarsmall{1}{2}{3}{4}+\scaleIntBscalarsmall{4}{3}{2}{1}\right]+\text{cyc}(2,3,4)
\end{equation}
We stress that the integrals appearing above are complicated by tensor integrals with many powers of loop momenta. However, as noted in the introduction, since both integrals are recursively one-loop, we can again apply a two-loop generalization of Passarino-Veltman for both the bubble and triangle integrals, stated in \eqn{eq:bubRed} and \eqn{eq:triRed}, respectively. With this, we proceed to the next step in the calculation.

\paragraph{\textbf{Reduction}} Just as with one-loop, we will now reduce the integrals of \eqn{eq:NLSM2loop} to the a basis of $D$-dimensional scalar integrals using the EMU loop reduction. The double-bubble contribution yields the following:
\begin{equation}
\label{eq:NLSM2bub}
\begin{aligned}
\scaleIntCsmall &= f_{\pi}^{-6}C^{\text{2box}}_{(12|34)} \left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{14}-s_{13}}{(D-1)^2}+s_{12}\right)\right]
\\
&+f_{\pi}^{-6}C^{\text{2box}}_{(12|43)} \left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{13}-s_{14}}{(D-1)^2}+s_{12}\right)\right]
\end{aligned}
\end{equation}
Likewise, we can perform a similar reduction to the dunce cap integrals -- but with a small twist. The double-bubble integral above is completely separable, which allows one to treat the tensor reduction of each loop integral as independent. This is not so for the ostrich-diagram integral. The ostrich-diagram carries an internal bubble, $I^D_2(q)$, with a loop dependent scale factor of $q=l_2+k_1$. Thus, we must first reduce the powers of $l_1$ and {then} perform a tensor reduction on all the remaining $l_2$ factors. Doing so yields the following result:

@@

Now that we have walked through our procedure for computing two-loop even point theory amplitudes with NLSM as an exemplar, we are prepared to proceed to the main results of the text. While the construction of DBIVA integrands is significantly more cumbersome than constructing the simple expressions of NLSM, the general procedure is exactly the same. The only differences being additional gauge independent state sums, and longer compute time needed for the tensor reduction.

@@

As we noted in the introduction, DBIVA tree-level amplitudes, which appear in the field theory limit of the abelianized open superstring, can be realized as a {double copy} between NLSM and sYM \cite{Cachazo:2014xea}, 
\begin{equation}
\mathcal{M}^{\text{DBIVA}} = \mathcal{A}^{\text{NLSM}} \otimes \mathcal{A}^{\text{sYM}}
\end{equation}
To carry out this construction at loop level, we simply would need to replace the color factors of NLSM with color-dual loop-level numerators, and then integrate the result. At present, this procedure can only be carried out beyond one-loop with NLSM and $\mathcal{N}=4$ sYM, for which color-dual representations are known through four-loop \cite{BCJLoop, GravityFour}. Indeed, in the next section we will use this as a check on our $\mathcal{N}=4$ DBIVA results of this section. Moreover, if we had access to color-dual representations for NLSM at two-loop, we could simply plug those into the sYM integrands constructed from simplified methods of supersymmetric sums \cite{SuperSum}, which would dramatically simplify our unitarity based construction.

While the double-copy procedure is presently not an option, the recursive structure of even point gauge theories saves us. As in the previous section where we computed NLSM amplitudes, the recursively one-loop structure permits us to only consider the four-point contacts when constructing the physical parts of the two-loop integrand. We will start by reproducing the known one-loop results from a completely $D$-dimensional framework, and then move onto our novel two-loop results.

@@

\text{Cut}\left(\!\scaleIntAvector{1}{2}{3}{4}\!\right) &= \sum_{ \text{states}}\mathcal{M}^{\gamma \gamma \gamma \gamma }_{(q_1|12|q_2)}\mathcal{M}^{\gamma \gamma \gamma \gamma }_{(\bar{q}_2|34|\bar{q}_1)} \equiv \text{Cut}(\mathcal{I}^{\text{1-loop}}_{N_\gamma} )

@@

\text{Cut}\left(\!\scaleIntAfermion{1}{2}{3}{4}\!\right)  &= \sum_{ \text{states}}\mathcal{M}^{\lambda \gamma \gamma \bar{\lambda} }_{(q_1|12|q_2)} \mathcal{M}^{\lambda \gamma \gamma \bar{\lambda} }_{(\bar{q}_2|34|\bar{q}_1)}\equiv \text{Cut}(\mathcal{I}^{\text{1-loop}}_{N_\lambda} )

@@

\text{Cut}\left(\!\scaleIntAScalar{1}{2}{3}{4}\!\right)  &= \sum_{ \text{states}}\mathcal{M}^{X \gamma \gamma \bar{X} }_{(q_1|12|q_2)}\mathcal{M}^{X \gamma \gamma \bar{X} }_{(\bar{q}_2|34|\bar{q}_1)}\equiv \text{Cut}(\mathcal{I}^{\text{1-loop}}_{N_X} )

@@

where exposed internal particles are taken to be on-shell. Above we have defined the internal momenta as $q_1 = l$ and $q_2 = -(l_1+k_{12})$. The vector and fermion contributions are rather complicated -- however, to get a sense of what pops out of this $D$-dimensional construction, we provide the scalar cut below as an example:

@@

\text{Cut}(\mathcal{I}^{\text{1-loop}})= 16(q_1 F_1F_2 q_1)(q_1 F_3F_4 q_1)

@@

Constructing the full amplitude is then just a matter of summing over all cut contributions, each weighted by symmetry factors $S_\alpha$ and the number, $N_\alpha$, of $\alpha$-type particles:

@@

\mathcal{M}^{\text{1-loop}} = \sum_{\alpha } \frac{N_\alpha}{S_{\alpha}}\int \frac{d^D l}{(2\pi)^D} \frac{\text{Cut}(\mathcal{I}^{\text{1-loop}}_{N_\alpha} )}{l^2(l+k_{12})^2} +\text{cyc}(2,3,4)

@@

\mathcal{M}^{\text{1-loop}} = \left[\frac{N_\gamma}{2}\!\!\scaleIntAvector{}{}{}{}-N_\lambda\!\!\scaleIntAfermion{}{}{}{} +N_X\!\!\scaleIntAScalar{}{}{}{} \!\!\right] +\text{cyc}(2,3,4)

@@

In order to capture all the tensor structures that survive after integration, including the evanescent contributions, we will map our results to the basis of operators specificed in \sect{sec:basisT}:

@@

\mathcal{M}^{\text{photon-EFT}} = \sum_{x,y} a_{(x,y)}^{F^2F^2}\mathcal{O}^{F^2F^2}_{(x,y)}+a_{(x,y)}^{F^4}\mathcal{O}^{F^4}_{(x,y)}+a_{(x,y)}^{F^3}\mathcal{O}^{F^3}_{(x,y)}

@@

\mathcal{M}^{\text{photon-EFT}}_{\text{1-loop}} = a_{(2,0)}^{F^2F^2}\mathcal{O}^{F^2F^2}_{(2,0)}+a_{(2,0)}^{F^4}\mathcal{O}^{F^4}_{(2,0)}+a_{(0,1)}^{F^2F^2}\mathcal{O}^{F^2F^2}_{(0,1)}+a_{(0,1)}^{F^4}\mathcal{O}^{F^4}_{(0,1)}

@@

a_{(2,0)}^{F^2F^2}&=\frac{i}{(4\pi)^2}\frac{1}{\epsilon}\left[\frac{N_\gamma }{75}(-60+61\epsilon)+\frac{N_X }{225}(30+47\epsilon)-\frac{N_\lambda }{75}(15+\epsilon)\right]+\mathcal{O}(\epsilon)

@@

a_{(0,1)}^{F^2F^2}&=\frac{i}{(4\pi)^2}\frac{1}{\epsilon}\left[\frac{N_\gamma }{3}(6+4\epsilon)-\frac{N_\lambda}{3}\epsilon\right]+\mathcal{O}(\epsilon)

@@

a_{(2,0)}^{F^4}&=\frac{i}{(4\pi)^2}\frac{1}{\epsilon}\left[\frac{N_\gamma }{75}(105+17\epsilon)+\frac{N_X }{225}(15+16\epsilon)+\frac{N_\lambda }{150}(15-19\epsilon)\right]+\mathcal{O}(\epsilon)

@@

a_{(0,1)}^{F^4}&=\frac{i}{(4\pi)^2}\frac{1}{\epsilon}\left[\frac{N_\gamma }{25}(-20+22\epsilon)-\frac{N_X }{225}(30+32\epsilon)-\frac{N_\lambda }{25}(5+2\epsilon)\right]+\mathcal{O}(\epsilon)

@@

\paragraph{\textbf{Projection}} While the expressions above capture the full behavior of the photon amplitudes, they obscure the 4D physics captured by spinor helicity variables. Rather than plugging in explicit values for $D$ in the integral, it can be more informative to first project down onto a 4D basis of states, leaving the internal dimensional dependence untouched. Indeed, below we can see the affect of plugging in all-plus helicity configurations into the evaluated one-loop integrals above:

@@

\mathcal{M}^{\text{DBIVA}} _{(--++)}&=\frac{i}{\epsilon} \frac{[12]^2\langle34\rangle^2}{(4\pi)^2}\left[\frac{N_\gamma}{2}s_{12}^2+\left(\frac{N_\gamma}{5}+\frac{N_\lambda}{20}+\frac{N_X}{30}\right)(s_{13}^2+s_{14}^2)\right]+\mathcal{O}(\epsilon^0)

@@

\mathcal{M}^{\text{DBIVA}}_{(++++)}&= -\frac{i}{(4\pi)^2}\frac{1}{60}\left(N_\gamma+N_X-N_\lambda\right) (s_{12}^4+s_{13}^4+s_{14}^4)\frac{[12][34]}{\langle12\rangle\langle 34\rangle}+\mathcal{O}(\epsilon^1) \label{eq:generalDBI1loop}

@@

As in the previous section, exposed legs implicitly sum over internal states. The grey blobs above represent $D$-dimensional $t_8F^4$ operator insertions from the four-point BI tree amplitudes, which we labelled as $\mathcal{M}^{\gamma\gamma\gamma\gamma}_{(1234)}$. We give the internal loop momenta the same internal labels as we did the pions in \eqn{eq:NLSM2Bub} and \eqn{eq:NLSMDunce}, giving us the following integrals to evaluate for two-loop pure BI, 

@@

Luckily, the state-sewing for maximal supersymmetry is dramatically more simple than less than maximal supersymmetry \cite{BDKUniarityReview,BRY}. This is most easily seen by considering the covariant operators we defined for one-loop DBIVA amplitudes. When one applies the conditions for maximal supersymmetry, stated below,
D=10 \qquad N_\lambda &=1 \qquad N_X=0
D=6 \qquad N_\lambda &=2 \qquad N_X=1
D=4 \qquad N_\lambda &=4 \qquad N_X=3
D=3 \qquad N_\lambda &=8 \qquad N_X=8
then the state sum is {completely independent of loop momenta} and precisely reproduces the supersymmetric operator $s_{12}^2 (t_8F^4)$ when cut along the $s_{12}$-channel.  This statement holds covariantly in general dimension. Concretely, we find that for theories with maximal supersymmetry:
\sum_{\text{states}}(t_8F^4)^{(\text{max})}_{(12l_1l_2)}(t_8F^4)^{(\text{max})}_{(\bar{l}_1\bar{l}_234)} = s_{12}^2 (t_8F^4)^{(\text{max})}_{(1234)}
This can similarly be used in the integrand construction $\mathcal{N}=4$ super-Yang-Mills, which has been computed to six-loop order \cite{Carrasco:2021otn}. In the case of maximal supersymmetry in $D=4$, we can write the  $(t_8F^4)^{(\text{max})}_{(1234)}$ operator as a supersymmetric delta function with the all-plus permutation invariant introduced previously:
\mathcal{M}^{\mathcal{N}=4\text{DBIVA}}_{(1234)} = \delta^{(8)}{(Q)} \frac{[12][34]}{\langle 12\rangle \langle 34\rangle} \equiv (t_8F^4)^{(\text{max})}_{(1234)}\Big|_{D=4}
where the delta function is a Grassmann valued polynomial of spinor-helicity variables:
\delta^{(8)}{(Q)} = \prod_{a=1}^4\sum_{i\neq j} \langle ij \rangle \eta_i^a\eta_j^a
By applying this supersymmetric state sum, we find that the integrands for two-loop $\mathcal{N}=4$ DBIVA is trivially easy to construct - even simpler than NLSM integrands. Below we represent an internal on-shell superfield with a green line, and obtain the following integrand for the double-bubble:
\begin{equation}\label{eq:N42bub}
\text{Cut}\left(\scaleIntCtune{}{hgreen}{}{hgreen}\right)=\sum_{\text{states}}  (t_8F^4)^{(\text{max})}_{(1234)} (t_8F^4)^{(\text{max})}_{(1234)} (t_8F^4)^{(\text{max})}_{(1234)}= s_{12}^4 (t_8 F^4)
and similarly so for the ostrich-diagram integral contribution:
\begin{equation}\label{eq:N4dunce}
\text{Cut}\left(\scaleIntBtune{}{}{}{}{hgreen}{hgreen}{hgreen}{hgreen}\,\,\right)=\sum_{\text{states}}  (t_8F^4)^{(\text{max})}_{(1234)} (t_8F^4)^{(\text{max})}_{(1234)} (t_8F^4)^{(\text{max})}_{(1234)}=s_{12}^2 \tau^{(2)}_2\tau^{(1)}_1(t_8 F^4)\,.
Since there are no loop momenta interfering with the tensor structures of the external photons, the result of integration will just be proportional to a $(t_8F^4)$ tensor, which is manifestly $U(1)$ duality invariant. Thus, as promised, adding in $\mathcal{N}=4$ states cancels the $U(1)$ anomaly present in the pure Born-Infeld $S$-matrix. After applying the tensor reduction to the ostrich-diagram, we obtain the following expression for the two diagrams:
\scaleIntCtune{}{hgreen}{}{hgreen} &= s_{12}^4 (I_2^{D}(k_{12}))^2(t_8 F^4)  
\scaleIntBtune{}{}{}{}{hgreen}{hgreen}{hgreen}{hgreen} \,\,\,\,&= \frac{s_{12}^3}{3}[I_3\circ I_2]^{D}(k_{12})(t_8 F^4)
This is easily evaluated in $D=4-2\epsilon$, from which we find the following expression for the leading order divergence of the four-photon two-loop amplitude in $\mathcal{N}=4$ DBIVA theory:
\mathcal{M}^{\mathcal{N}=4\text{ DBIVA}}_{\text{2-loop}} = -\frac{1}{\epsilon^2}\frac{1}{768\pi^4}(s_{12}^4+s_{13}^4+s_{14}^4)(t_8 F^4) + \mathcal{O}(\epsilon^{-1})
With this result in hand, we will now demonstrate that the same calculation that we have performed via generalized unitarity can be reproduced using loop-level double copy construction. 
\subsection{DBIVA via double copy}\label{sec:DBIvDC}
The calculation performed above was completely agnostic to the known tree-level relationship of DBIVA amplitudes as a double copy of NLSM and super Yang-Mills. As we will now show, the amplitude above can be equivalently produced using the two-loop color-dual numerators of $\mathcal{N}=4$ sYM, and the NLSM integrands constructed earlier in this section. This observation provides further evidence for the consistency of double-copy construction at multi-loop order in perturbation theory, and serves as an existence proof for color-dual NLSM numerators at two-loop.

>>>>

\newcommand{\numScalars}{Z_X}
\newcommand{\numPhotons}{Z_\gamma}
\newcommand{\numFerms}{Z_\lambda}

@@

\begin{equation}\label{eq:NLSMOstrich}
\begin{aligned}
\text{Cut}\left(\! \scaleIntBscalarsmall{1}{2}{3}{4} \! \right)&=\sum_{\text{states}}\mathcal{A}^{\text{NLSM}}_{(2|q_4\bar{q}_3|\bar{q}_1)}\mathcal{A}^{\text{NLSM}}_{(1|\bar{q}_4q_3|\bar{q}_2)}\mathcal{A}^{\text{NLSM}}_{(q_2|34|q_1)}
\\
&=C^{\text{Xbox}}_{([12]|34)}\left[\tau^{(3)}_1 \tau^{(2)}_3\tau^{(1)}_4+\tau^{(3)}_1 \tau^{(2)}_4\tau^{(1)}_3+\tau^{(3)}_2 \tau^{(2)}_3\tau^{(1)}_4+\tau^{(3)}_2 \tau^{(2)}_4\tau^{(1)}_3\right]
\\
&-\left(C^{\text{2box}}_{(12|34)}\tau^{(3)}_1+C^{\text{2box}}_{(12|43)}\tau^{(3)}_2\right) \left[ \tau^{(2)}_3\tau^{(1)}_3+ \tau^{(2)}_4\tau^{(1)}_4\right] \,.
\end{aligned}
\end{equation}
The kinematic variables $\tau^{(i)}_j $ and $\tau_{ij}$ are the same, except we have made the replacement $p_i \rightarrow q_i$. The full two-loop NLSM amplitude can thus be computed by summing over the distinct labels of the resulting integrals, each weighted by suitable internal symmetry factors:
\begin{equation}
\label{eq:NLSM2loop}
\mathcal{A}^{\text{NLSM}}_{\text{2-loop}}=\frac{1}{4}\left[ \scaleIntCsmall \right]+ \frac{1}{2}\left[\scaleIntBscalarsmall{1}{2}{3}{4}+\scaleIntBscalarsmall{4}{3}{2}{1}\right]+\text{cyc}(2,3,4)
\end{equation}
We stress that the integrals appearing above are complicated by tensor integrals with many powers of loop momenta. However, as noted in the introduction, since both integrals are recursively one-loop, we can again apply a two-loop generalization of Passarino-Veltman for both the bubble and triangle integrals, stated in \eqn{eq:bubRed} and \eqn{eq:triRed}, respectively. With this, we proceed to the next step in the calculation.

\paragraph{\textbf{Reduction}} Just as with one-loop, we will now reduce the integrals of \eqn{eq:NLSM2loop} to the a basis of $D$-dimensional scalar integrals using the EMU loop reduction. The double-bubble contribution yields the following:
\begin{equation}
\label{eq:NLSM2bub}
\begin{aligned}
\scaleIntCsmall &= f_{\pi}^{-6}C^{\text{2box}}_{(12|34)} \left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{14}-s_{13}}{(D-1)^2}+s_{12}\right)\right]
\\
&+f_{\pi}^{-6}C^{\text{2box}}_{(12|43)} \left[\frac{(s_{12}I_2^D(k_{12}))^2}{2}\left(\frac{s_{13}-s_{14}}{(D-1)^2}+s_{12}\right)\right]
\end{aligned}
\end{equation}
Likewise, we can perform a similar reduction to the ostrich integrals -- but with a small twist. The double-bubble integral above is completely separable, which allows one to treat the tensor reduction of each loop integral as independent. This is not so for the ostrich-diagram integral. The ostrich-diagram carries an internal bubble, $I^D_2(q)$, with a loop dependent scale factor of $q=l_2+k_1$. Thus, we must first reduce the powers of $l_1$ and {then} perform a tensor reduction on all the remaining $l_2$ factors. Doing so yields the following result:

@@

Now that we have walked through our procedure for computing two-loop even point theory amplitudes with NLSM as an exemplar, we are prepared to proceed to the main results of the text. While the construction of DBIVA integrands is more involved than constructing the simple expressions of NLSM, the general procedure is exactly the same. The only differences being additional gauge independent state sums, and longer compute time needed for the tensor reduction.

@@

As we noted in the introduction, DBIVA tree-level amplitudes, which appear in the field theory limit of the abelianized open superstring, can be realized as a {double copy} between NLSM and sYM \cite{Cachazo:2014xea}, 
\begin{equation}
\mathcal{M}^{\text{DBIVA}} = \mathcal{A}^{\text{NLSM}} \otimes \mathcal{A}^{\text{sYM}}
\end{equation}
To carry out this construction at the (multi-)loop level, we simply would need to replace the color factors of NLSM with color-dual loop-level numerators, and then integrate the result. In the case of $\mathcal{N}=4$ sYM, color-dual representations are known through four-loop \dj{fixReferences...} \cite{BCJLoop, GravityFour}. Indeed, in  \sect{sec:DBIvDC} we will use use double-copy to verify the $\mathcal{N}=4$ DBIVA results we construct here via unitarity.  \dj{Can't we just use susy-state sum methods on tree-level DBIVA amplitudes?  i.e. we can use KLT on the cuts. Will think -JJ} If we had access to color-dual representations for NLSM at two-loop, we could simply plug those into the sYM integrands constructed from simplified methods of supersymmetric sums \cite{SuperSum}, which would dramatically simplify our unitarity based construction.

As in the previous section where we computed NLSM amplitudes, the recursively one-loop structure will permits us to only consider the four-point contacts when constructing the physical parts of the two-loop integrand. We will start by reproducing the known one-loop results from a completely $D$-dimensional framework, and then move onto our novel two-loop results.

@@

\text{Cut}\left(\!\scaleIntAvector{1}{2}{3}{4}\!\right) &= \sum_{ \text{states}}\mathcal{M}^{\gamma \gamma \gamma \gamma }_{(q_1|12|q_2)}\mathcal{M}^{\gamma \gamma \gamma \gamma }_{(\bar{q}_2|34|\bar{q}_1)} \equiv \text{Cut}(\mathcal{I}^{\text{1-loop}}_{\gamma} )

@@

\text{Cut}\left(\!\scaleIntAfermion{1}{2}{3}{4}\!\right)  &= \sum_{ \text{states}}\mathcal{M}^{\lambda \gamma \gamma \bar{\lambda} }_{(q_1|12|q_2)} \mathcal{M}^{\lambda \gamma \gamma \bar{\lambda} }_{(\bar{q}_2|34|\bar{q}_1)}\equiv \text{Cut}(\mathcal{I}^{\text{1-loop}}_{\lambda} )

@@

\text{Cut}\left(\!\scaleIntAScalar{1}{2}{3}{4}\!\right)  &= \sum_{ \text{states}}\mathcal{M}^{X \gamma \gamma \bar{X} }_{(q_1|12|q_2)}\mathcal{M}^{X \gamma \gamma \bar{X} }_{(\bar{q}_2|34|\bar{q}_1)}\equiv \text{Cut}(\mathcal{I}^{\text{1-loop}}_{X} )

@@

where exposed internal particles are taken to be on-shell. Above we have defined the internal momenta as $q_1 = l$ and $q_2 = -(l_1+k_{12})$. While the vector and fermion cut contributions are straightforward, the scalar cut has the virtue of being compact enough to typeset as an instructive example:

@@

\text{Cut}(\mathcal{I}^{\text{1-loop}}_{\numScalars})= 16(q_1 F_1F_2 q_1)(q_1 F_3F_4 q_1)\,.

@@

\dj{We want a subscript $X$ like $\mathcal{I}^{\text{1-loop}}_{\numScalars} $ instead of $\mathcal{I}^{\text{1-loop}}$ here right?}
Constructing the full amplitude is then just a matter of summing over all cut contributions, each weighted by symmetry factors $S_\alpha$ and the number, $Z_\alpha$, of $\alpha$-type particles:

@@

\mathcal{M}^{\text{1-loop}} = \sum_{\alpha } \frac{N_\alpha}{S_{\alpha}}\int \frac{d^D l}{(2\pi)^D} \frac{\text{Cut}(\mathcal{I}^{\text{1-loop}}_{\alpha} )}{l^2(l+k_{12})^2} +\text{cyc}(2,3,4)

@@

\mathcal{M}^{\text{1-loop}} = \left[\frac{\numPhotons}{2}\!\!\scaleIntAvector{}{}{}{}-\numFerms\!\!\scaleIntAfermion{}{}{}{} +\numScalars\!\!\scaleIntAScalar{}{}{}{} \!\!\right] +\text{cyc}(2,3,4)

@@

In order to capture all the tensor structures that survive after integration, including the evanescent contributions, we will map our results to the basis of tensor structures identified in \sect{sec:basisT}:

@@

\mathcal{M}^{\text{photon-EFT}} = \sum_{x,y} a_{(x,y)}^{F^2F^2}\mathcal{T}^{F^2F^2}_{(x,y)}+a_{(x,y)}^{F^4}\mathcal{T}^{F^4}_{(x,y)}+a_{(x,y)}^{F^3}\mathcal{T}^{F^3}_{(x,y)}

@@

\mathcal{M}^{\text{photon-EFT}}_{\text{1-loop}} = a_{(2,0)}^{F^2F^2}\mathcal{T}^{F^2F^2}_{(2,0)}+a_{(2,0)}^{F^4}\mathcal{T}^{F^4}_{(2,0)}+a_{(0,1)}^{F^2F^2}\mathcal{T}^{F^2F^2}_{(0,1)}+a_{(0,1)}^{F^4}\mathcal{T}^{F^4}_{(0,1)}

@@

a_{(2,0)}^{F^2F^2}&=\frac{i}{(4\pi)^2}\frac{1}{\epsilon}\left[\frac{\numPhotons }{75}(-60+61\epsilon)+\frac{\numScalars }{225}(30+47\epsilon)-\frac{\numFerms }{75}(15+\epsilon)\right]+\mathcal{O}(\epsilon)

@@

a_{(0,1)}^{F^2F^2}&=\frac{i}{(4\pi)^2}\frac{1}{\epsilon}\left[\frac{\numPhotons }{3}(6+4\epsilon)-\frac{\numFerms}{3}\epsilon\right]+\mathcal{O}(\epsilon)

@@

a_{(2,0)}^{F^4}&=\frac{i}{(4\pi)^2}\frac{1}{\epsilon}\left[\frac{\numPhotons }{75}(105+17\epsilon)+\frac{\numScalars }{225}(15+16\epsilon)+\frac{\numFerms }{150}(15-19\epsilon)\right]+\mathcal{O}(\epsilon)

@@

a_{(0,1)}^{F^4}&=\frac{i}{(4\pi)^2}\frac{1}{\epsilon}\left[\frac{\numPhotons }{25}(-20+22\epsilon)-\frac{\numScalars }{225}(30+32\epsilon)-\frac{\numFerms }{25}(5+2\epsilon)\right]+\mathcal{O}(\epsilon)

@@

\paragraph{\textbf{Projection}} While the expressions above capture the full behavior of the photon amplitudes, they obscure the 4D physics that we can now expose using spinor helicity variables. Rather than plugging in explicit values for $D$ in the integral, it will be more informative to first project down onto an external 4D basis of states, leaving the internal dimensional dependence untouched. Indeed, below we can see the affect of plugging in all-plus helicity configurations into the evaluated one-loop integrals above:

@@

\mathcal{M}^{\text{DBIVA}} _{(--++)}&=\frac{i}{\epsilon} \frac{[12]^2\langle34\rangle^2}{(4\pi)^2}\left[\frac{\numPhotons}{2}s_{12}^2+\left(\frac{\numPhotons}{5}+\frac{\numFerms}{20}+\frac{\numScalars}{30}\right)(s_{13}^2+s_{14}^2)\right]+\mathcal{O}(\epsilon^0)

@@

\mathcal{M}^{\text{DBIVA}}_{(++++)}&= -\frac{i}{(4\pi)^2}\frac{1}{60}\left(\numPhotons+\numScalars-\numFerms\right) (s_{12}^4+s_{13}^4+s_{14}^4)\frac{[12][34]}{\langle12\rangle\langle 34\rangle}+\mathcal{O}(\epsilon^1) \label{eq:generalDBI1loop}

@@

As in the previous section, exposed legs implicitly sum over internal states. The grey blobs above represent $D$-dimensional $t_8F^4$ operator insertions from the four-point BI tree amplitudes, which we labelled as $\mathcal{M}^{\gamma\gamma\gamma\gamma}_{(1234)}$. We give the internal loop momenta the same internal labels as we did the pions in \eqn{eq:NLSM2Bub} and \eqn{eq:NLSMOstrich}, giving us the following integrals to evaluate for two-loop pure BI, 

@@

Luckily, the state-sewing for maximal supersymmetry is dramatically more simple than less than maximal supersymmetry \cite{BDKUniarityReview,BRY}. This is most easily seen by considering the covariant operators we defined for one-loop DBIVA amplitudes. When one applies the conditions for maximal supersymmetry, stated below,
\begin{align}
D=10 \qquad \numFerms &=1 \qquad \numScalars=0
\\
D=6 \qquad \numFerms &=2 \qquad \numScalars=1
\\
D=4 \qquad \numFerms &=4 \qquad \numScalars=3
\\
D=3 \qquad \numFerms &=8 \qquad \numScalars=8
\end{align}
then the state sum is {completely independent of loop momenta} and precisely reproduces the supersymmetric operator $s_{12}^2 (t_8F^4)$ when cut along the $s_{12}$-channel.  This statement holds covariantly in general dimension. Concretely, we find that for theories with maximal supersymmetry:
\begin{equation}
\sum_{\text{states}}(t_8F^4)^{(\text{max})}_{(12l_1l_2)}(t_8F^4)^{(\text{max})}_{(\bar{l}_1\bar{l}_234)} = s_{12}^2 (t_8F^4)^{(\text{max})}_{(1234)}
\end{equation}
This can similarly be used in the integrand construction $\mathcal{N}=4$ super-Yang-Mills, which has been computed to six-loop order \cite{Carrasco:2021otn}. In the case of maximal supersymmetry in $D=4$, we can write the  $(t_8F^4)^{(\text{max})}_{(1234)}$ operator as a supersymmetric delta function with the all-plus permutation invariant introduced previously:
\begin{equation}
\label{dblBubbleCutDBIVA}
\mathcal{M}^{\mathcal{N}=4\text{DBIVA}}_{(1234)} = \delta^{(8)}{(Q)} \frac{[12][34]}{\langle 12\rangle \langle 34\rangle} \equiv (t_8F^4)^{(\text{max})}_{(1234)}\Big|_{D=4}
\end{equation}
where the delta function is a Grassmann valued polynomial of spinor-helicity variables:
\begin{equation}
\label{ostrichCutDBIVA}
\delta^{(8)}{(Q)} = \prod_{a=1}^4\sum_{i\neq j} \langle ij \rangle \eta_i^a\eta_j^a
\end{equation}
By applying this supersymmetric state sum, we find that the integrands for two-loop $\mathcal{N}=4$ DBIVA is trivially easy to construct - even simpler than NLSM integrands. Below we represent an internal on-shell superfield with a green line, and obtain the following integrand for the double-bubble:
\begin{equation}\label{eq:N42bub}
\text{Cut}\left(\scaleIntCtune{}{hgreen}{}{hgreen}\right)=\sum_{\text{states}}  
(t_8 F^4)^{(\text{max})}_{(1234)} (t_8 F^4)^{(\text{max})}_{(1234)} 
(t_8 F^4)^{(\text{max})}_{(1234)}= s_{12}^4 \left( t_8 F^4 \right)
\end{equation}
and similarly so for the ostrich-diagram integral contribution:
\begin{equation}\label{eq:N4dunce}
\text{Cut}\left(\scaleIntBtune{}{}{}{}{hgreen}{hgreen}{hgreen}{hgreen}\,\,\right)=\sum_{\text{states}}  \left(t_8 F^4\right)^{\left(\text{max}\right)}_{(1234)} \left(t_8 F^4\right)^{(\text{max})}_{(1234)} (t_8 F^4)^{(\text{max})}_{(1234)}=s_{12}^2 \tau^{(2)}_2\tau^{(1)}_1(t_8 F^4)\,.
\end{equation}
\dj{Relabel actual cuts and lets check the RHS here of the ostrich.  I get: $s_{12}^2 \left(\tau^{(1)}_{\bar{2}} \equiv (k_1-q_2)^2 \right)^2 (t_8 F^4)$ both via KLT on the cuts and via your sewing rule.}

We should point out an additional verification that can occur for any SUSY amount of DBIVA .  Any DBIVA cut is quite simply a sum over various color-ordered cuts of supersymmetric gauge theory integrands weighted with scalar dressings instead of color.   What this means is that we can recycle multiloop SYM integrands to verify our cuts.  In general this is because double-copy works at tree-level, and we can always write the Jacobi-satisfying numerators into ordered-amplitudes giving us a KLT between cut-integrands.  When we cut to four-point amplitudes as we do here this is particularly simple, yielding:
\begin{align}
\text{Cut}({\mathcal{N}-\text{DBIVA}})&= \sum_\text{states} \prod_i A^{\mathcal{N}-\text{DBIVA}}(p^i_1,p^i_2,p^i_3,p^i_4)\\
&= \sum_\text{states} \prod_i  ( p^{(i)}_1 \cdot p^{(i)}_2) ( p^{(i)}_2 \cdot p^{(i)}_3)   A^{\mathcal{N}-\text{DBIVA}}(p^{(i)}_1,p^{(i)}_2,p^{(i)}_3,p^{(i)}_4)\\
&= \left( \prod_j  \left( p^{(j)}_1 \cdot p^{(j)}_2\right) \left( p^{(j)}_2 \cdot p^{(j)}_3\right)  \right) \sum_\text{states}   \prod_i  A^{\mathcal{N}- \text{SYM}}(p^{(i)}_1,p^{(i)}_2,p^{(i)}_3,p^{(i)}_4)\\
&= \left( \prod_j  \left( p^{(j)}_1 \cdot p^{(j)}_2\right) \left( p^{(j)}_2 \cdot p^{(j)}_3\right) \right)  \sum_\text{states} \text{Cut}({\mathcal{N}- \text{DBIVA}})
\end{align}
The second line follows from the double-copy structure of four-point amplitudes in DBIVA, where:
\begin{align}
A^{\mathcal{N}-\text{DBIVA}}(1,2,3,4) = s t A^{\mathcal{N}- \text{SYM}}
\end{align}

Carrying out the verifications of \eqn{dblBubbleCutDBIVA} and \eqn{ostrichCutDBIVA} in the case of maximally supersymmetric Yang-Mills in four-dimensions is trivial -- only one (non-vanishing) diagram contributes to each cut. We provide the details in an appendix which may be of pedagogic interest.
